BugTracking: A tool to assist in the Bug Triage Process

### 2016-01-13 OSS_2016/paper.tex
Abstract...

\title*{BugTracking: A tool to assist in the Bug Triage Process}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Gema Rodriguez\inst{1}\and Jesus M. Gonzalez-Barahona\inst{1}}
%\and Name of Author\inst{2}}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{\texttt{gerope@libresoft.es}, \texttt{jgb@gsyc.es}
\and GSyC/LibreSoft, Universidad Rey Juan Carlos}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle
\section{Introduction} 
\label{sec:1}

>>>>

\title*{BugTracking: A tool to assist in the Bug Triage Process}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Gema Rodriguez\inst{1}, Jesus M. Gonzalez-Barahona \and Gregorio Robles\inst{1}}
%\and Name of Author\inst{2}}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{\texttt{gerope@libresoft.es}, \texttt{jgb@gsyc.es}
\and GSyC/LibreSoft, Universidad Rey Juan Carlos}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\begin{abstract}
	In most software projects, but in particular in almost all free, open source software projects, issue tracking systems are used for recording many different kinds of issues: bug reports, feature requests, maintenance tickets, and even design discussions. Identifying which of those issues are bug reports, is not a trivial task. When researchers want to conduct some study on the bug reports managed by a software development project, they need to first of all to perform this identification.

	The job for researchers here is very different from the bug triaging that developers do. In the latter case, people with a lot of experience in the project make a decission based on the information available at that time (maybe just a short comment by some user), asking if needed for more details. In the former case, researchers are usually not that experienced in the project, but they have at their disposal all the information produced, until the moment the issue was closed. This may include not only all comments and actions on the issue tracking system, but for examples, discusions about a fix in the code review system, or the final fixing patch in the source code management system. Having all that information conveyed to the researchers in an easy, flexible and quick way accelerates and makes much more reliable their decission making process. This simplifies large scale manual analysis of issues (in the hundreds or thousands), helping researchers to ensure that they are really working with what they intend to work: bug reports.

	This paper presentes a tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not. The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports, making the process easier, faster, and more reliable.
\end{abstract}

\section{Introduction}
\label{sec:1}
